### 2015-05-27 doc/manual/inputParameters.tex
Added profiles examples

>>>>

The resolution parameters each have 3 associated sfincsScan parameters
which are used for convergence scans ({\ttfamily scanType} = 1): {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}.
The first two of these set the range by which the associated resolution parameter is scaled
in a convergence scan. The {\ttfamily ...NumRuns} parameter sets the number of values tried in a
convergence scan. The code attempts to space the values evenly in a logarithmic
sense, as in Matlab's 'logspace' function. For example, the following settings\\
{\ttfamily
    Nxi = 20\\
!ss NxiMinFactor = 0.5\\
!ss NxiMaxFactor = 2.0\\
!ss NxiNumRuns = 3\\
}
would mean the values {\ttfamily Nxi} = 10, 20, and 40 would be tried in a convergence scan.
If you don't want to scan a variable in a convergence scan, set the associated
{\ttfamily ...NumRuns} parameter to 0, or do not include this parameter in the input file.
For each resolution parameter ({\ttfamily Ntheta}, {\ttfamily Nzeta}, {\ttfamily Nxi}, etc.), the value itself is read by
Fortran and so should not be preceded by {\ttfamily !ss}.  However the {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}
quantities are read by \sfincsScan~and so must be preceded by {\ttfamily !ss}
